Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-07-06 Scripts/Initial_Analysis.Rmd
changes to functions to work on hall

  # Loads species data for all ensembles
  Spp_Dist <- bind_rows(
    lapply(
      ensemble_list,
      read_dbem_ens,
      taxon_key = taxon_key,
      year = year,
      data_type = data_type,
       model = "GFDL",
      rcp = "85",
      path = "NA",
      my_path = F
    )
  )

@@

  # Estimate Area index and % change
  Per_Ghange_D <- full_join(Territory_T,
                            Neighbour_T, 
                            by = c("Name","taxon_key","year","ensemble")
  ) %>%
    rowwise() %>%
    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per Neighbours
    distinct() %>% # Removes false duplicates from `full_join()`
    rename(eez_name = Name,
           eez_neighbour =eez_name,
           n_spp_Country = n_spp_eez.x,
           n_spp_Neighbour = n_spp_eez.y) %>% 
    mutate(area_index = n_spp_Country/Spp_Total) %>% 
    # Determine the three time frames for comparrison
    mutate(
      time_step = ifelse(year < hist_y,"historical",
                         ifelse(year >= 2021 & year <= 2040, "early",
                                ifelse(year >= 2041 & year <= 2060, "mid","NA")
                         )
      )
    ) %>%
    filter(time_step != "NA") %>% 
    # Time mean and sd
    ungroup() %>% 
    group_by(taxon_key,ensemble,eez_name,eez_neighbour,time_step) %>% 
    summarise_at(vars("area_index"),
                 c(temporal_mean=mean,
                   temporal_sd=sd)
    ) %>% 
    # ensemble mean and sd
    group_by(taxon_key,eez_name,eez_neighbour,time_step) %>%
    summarise_at(vars("temporal_mean"),
                 c(ensemble_mean=mean,
                   ensemble_sd=sd),
                 na.rm=T
    )

@@

  # Save Result
  name <- paste("proportion_",taxon_key,".csv",sep="")
  path_name <- paste(my_path("R",extra_path = "Proportion_n"),name,sep= "")

@@

# Last year of "historic" data
Historic_year = 2000

@@

  # Reads taxon data
  proportion_data <- fread(paste(my_path("R",extra_path = "Proportion/"),"proportion_",taxon_key,".csv", sep=""))

  if(links == "y"){
    # summarizes by country and neighbour
    country_summary <- proportion_data %>% 
      group_by(taxon_key,eez_name,eez_neighbour,time_step) %>% 
      summarise(
        mean_spp = mean(ensamble_mean,na.rm=T) # average spp change from all countries sharing
      )

@@

 proportion_change <- eez %>% 
   gather("variable","value",n_spp:sd_spp) %>% 
   spread(time_step,value) %>% 
   mutate_at(vars(
     "per_mid" = mid,
     "per_end" = n_end),
            funs(round((((.-historical)/historical))*100,2))
   )

@@

# Get taxon list
Taxon_List <- list.files(paste(my_path("R"),"Proportion",sep=""))

@@

# Run results
results <- PropChange(Taxon_List, links="y") %>% 
  mutate(per_mid_plot =ifelse(per_mid >= 50, 50,
                           ifelse(per_mid <= -50,-50,per_mid)
                           )
         )

@@

# The path
path_world <- my_path("G", extra_path = "Spatial/SAU/SAU_Shapefile")

@@

eez_centroid <- my_path("D",extra_path = "Spatial",name = "eez_centroids.csv",read = T)

@@

# Prepare data from results
Data <- results %>% 
  # get coords for sources
  left_join(eez_centroid,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(eez_centroid,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_mid = ifelse(is.na(per_mid_plot),0,per_mid_plot)
  ) %>% 
  drop_na() %>%
  filter(
    variable == "mean_spp"#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

@@

gc()# clean ram

x <- ggplot() +
  geom_sf(data = subset(World_map, sovereignt != "Antarctica"), size = 0.1, fill = "gray90", col = "gray90") +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray70") +
  geom_point(data = subset(Data, per_mid < 0),
             aes(start_lon,
                 start_lat,
                 col = per_mid),
             size = 0.05,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(paths, per_mid > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_mid
            ),
            size = 0.3,
            arrow = arrow(length = unit(0.009, "npc"),
                          ends = "first"),
            show.legend = NA) +
  ggtheme_map() +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Data$per_mid)),
    breaks = seq(0,max(Data$per_mid),5),
    # option="magma",
    direction = 1
  ) +
  ggsave("figure_connections_n50.png",
         width = 10,
         height = 6,
         units = "in"
  )

>>>>

  # Loads species data for all ensembles
  Spp_Dist <- bind_rows(
    lapply(
      ensemble_list,
      read_dbem_ens,
      taxon_key = taxon_key,
      year = year_df$year,
      data_type = data_type,
      model = "GFDL",
      rcp = "85",
      # path = "/Volumes/DATA/DATA",
      my_path = F
    )
  )

@@

  # Estimate Area index and % change
  Per_Ghange_D <- full_join(Territory_T,
                            Neighbour_T, 
                            by = c("Name","taxon_key","year","ensemble")
  ) %>%
    rowwise() %>%
    mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per Neighbours
    distinct() %>% # Removes false duplicates from `full_join()`
    rename(eez_name = Name,
           eez_neighbour =eez_name,
           n_spp_Country = n_spp_eez.x,
           n_spp_Neighbour = n_spp_eez.y) %>% 
    mutate(area_index = n_spp_Country/Spp_Total) %>% 
    # Determine the three time frames for comparrison
    mutate(
      time_step = ifelse(year < hist_y,"historical",
                         ifelse(year >= 2021 & year <= 2040, "early",
                                ifelse(year >= 2041 & year <= 2060, "mid","NA")
                         )
      )
    ) %>%
    filter(time_step != "NA") %>% 
    # Time mean and sd
    ungroup() %>% 
    group_by(taxon_key,ensemble,eez_name,eez_neighbour,time_step) %>% 
    summarise_at(vars("area_index"),
                 c(temporal_mean=mean,
                   temporal_sd=sd)
    ) %>% 
    # ensemble mean and sd
    group_by(taxon_key,eez_name,eez_neighbour,time_step) %>%
    summarise(
      ensemble_mean = mean(temporal_mean, na.rm = T),
      ensemble_sd = sd(temporal_mean, na.rm = T),
      ensemble_n = n()
    )

@@

  # Save Result
  name <- paste("proportion_",taxon_key,".csv",sep="")
  path_name <- paste(my_path("R",extra_path = "Proportion_2005"),name,sep= "")

@@

# Last year of "historic" data
Historic_year = 2005

@@

  # Reads taxon data
  proportion_data <- fread(paste(result_path,"Proportion/","proportion_",taxon_key,".csv", sep=""))

  if(links == "y"){
    # summarizes by country and neighbour
    country_summary <- proportion_data %>% 
      group_by(taxon_key,eez_name,eez_neighbour,time_step) %>% 
      summarise(
        mean_spp = mean(ensemble_mean,na.rm=T) # average spp change from all countries sharing
      )

@@

 proportion_change <- eez %>% 
   gather("variable","value",n_spp:sd_spp) %>% 
   spread(time_step,value) %>% 
   mutate_at(vars(
     "per_mid" = mid,
     "per_end" = n_end),
            funs(round((((.-historical)/.))*100,2))
   )

@@

# Get taxon list
Taxon_List <- list.files(paste(my_path("R"),"Propotion",sep=""))

@@

# Run results
Proportion_Results <- PropChange(Taxon_List, links="y") %>% 
  mutate(per_mid =ifelse(per_mid >= 25, 25,
                           ifelse(per_mid <= -25,-25,per_mid)
                           )
         )

@@

@@

@@

# Prepare data from results
Data <- results %>% 
  # get coords for sources
  left_join(eez_centroid,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(eez_centroid,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_mid = ifelse(is.na(per_mid),0,per_mid)
  ) %>% 
  drop_na() %>%
  filter(
    variable == "mean_spp"#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

@@

gc()# clean ram
x <- ggplot() +
  geom_sf(data = subset(World_map, sovereignt != "Antarctica"), size = 0.1, fill = "gray90", col = "gray90") +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray70") +
  geom_point(data = subset(Data, per_mid < 0),
             aes(start_lon,
                 start_lat,
                 col = per_mid),
             size = 0.05,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(paths, per_mid > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_mid
            ),
            size = 0.3,
            arrow = arrow(length = unit(0.009, "npc"),
                          ends = "first"),
            show.legend = NA) +
  ggtheme_map() +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,25),
    breaks = seq(0,25,5),
    # option="magma",
    direction = 1
  ) +
  ggsave("figure_connectionsc.png",
         width = 10,
         height = 6,
         units = "in"
  )
